---
title: "W06-2"
author: "Laura Giese, Johannes Schnell, Alena Schmid"
date: "18 Januar 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###script leave many out crossvalidation for improving LandUseClassification,
#input: - shapefile of all classes for ImageClassification
#       - rgbImage (example: caldern)
#workflow:
#       - leave out one main class (example: wasser) with n subclasses
#       - compute training_areas_shape_file containing all remaining classes
#       - calculate confusion matrix with otb_TrainImageClassifier
#       - calculate kappa from confusion matrix
#output: matrix with left-out-class and corresponding kappa value


```{r, echo = T}
### packages and functions
library(raster)
library(sp)
library(rgdal)
library(maptools)
library(prodlim)
#install.packages("maptools")

#function: Compute Kappa based on contingency table
#' 
#' @description
#' Compute Kappa index.
#'
#' @param ctable Contingency table
#'
#' @return Kappa index.
#'
compKappa <- function(ctable){
  ctable <- ctable/sum(ctable)
  categories <- nrow(ctable)
  
  # Fraction of agreement
  pagrm <- 0
  for(i in seq(categories)){
    pagrm <- pagrm + ctable[i,i]
  }
  
  # Expected fraction of agreement subject to the observed distribution
  pexpct <- 0
  for(i in seq(categories)){
    pexpct <- pexpct + sum(ctable[i,]) * sum(ctable[,i])
  }
  
  # Kappa index
  kappa <- (pagrm - pexpct)/(1 - pexpct)
  
  return(kappa)
}

#folder structure
setwd("C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa")
path_in = "C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/neu/"
path_out = "C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/"
path_trainImage = "C:/OSGeo4W64/bin/"
```

START

```{r, echo = T}
#load shape file
dbf_file = readOGR(paste0(path_in, "allclassfort.dbf"))

#klassenerkennung: which class is what?, not essential for script
g<-as.factor(dbf_file@data[,3])
f<-as.factor(dbf_file@data[,4])
d<-paste0(levels(g),"_",levels(f))

#create dateframe to pick classes (instead of random sampling)
df<-dbf_file@data[,3:4]
#create output matrix
kappa_out<-matrix(NA, 7, 2)

for (i in seq(1:7)){
#generating training area-shape files and leaving out one main class (stratified sampling) 
#instead of random sampling
  if (i == 1){
    class = "none"
    print(class)
    training_areas <- dbf_file
  } else if (i == 2){
  class = "wald"
  print(class)
  leaveout<-which(is.element(df[,1], c(0:99)))  
  }else if(i == 3){
    class = "felder"
    print(class)
    leaveout<- which(is.element(df[,1], c(100:199)))  
  }else if(i == 4){
    class = "siedlung"
    print(class)
    leaveout<-which(is.element(df[,1], c(200:299)))  
  }else if(i == 5){
    class = "wiesen"
    print(class)
    leaveout <- which(is.element(df[,1], c(300:399)))
  }else if(i == 6){
    class = "strassen"
    print(class)
    leaveout <- which(is.element(df[,1], c(400:499)))
  }else if(i == 7){
    class = "wasser"
    print(class)
    leaveout <- which(is.element(df[,1], c(500:599)))
  }
#as nothing is left out in first run (input: whole shape file), there´s no test data  
  if (i == 1){
    print(class)
  } else {
    #create training and test data sets
    test_areas <- dbf_file[leaveout,]
    training_areas <- dbf_file[-leaveout,]
    
    #savefiles as shape files
    writeOGR(test_areas, paste0(path_out, "test_areas_", i ,".shp"), 
             paste0(basename(paste0(path_out, "test_areas_", i, ".shp"))), 
             driver = "ESRI Shapefile", overwrite = T)
  }
  #savefiles as shape files
  writeOGR(training_areas, paste0(path_out, "training_areas_", i ,".shp"), 
           paste0(basename(paste0(path_out, "training_areas_", i, ".shp"))), 
           driver = "ESRI Shapefile", overwrite = T)
  
  #calculate confusion matrix with "TrainImageClassifier" as "otbcli_ComputeConfusionMatrix"
  #is not producing a nxn-matrix?!  
  system(paste0(path_trainImage,"otbcli_TrainImagesClassifier ",
                "-io.il C:/Users/Laura/Documents/Uni/Fernerkundung/ergebnisse/rgbRaster_cal.tif ",
                "-io.vd C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/training_areas_", i,".shp ",
                "-elev.default 0 ","-sample.mt 1000 ", "-sample.mv 1000 ", "-sample.bm 1 ", 
                "-sample.edg true ", "-sample.vtr 0.5 ", "-sample.vfn LN_New ", "-classifier rf ",
                "-classifier.rf.max 5 ", "-classifier.rf.min 10 ", "-classifier.rf.ra 0 ",
                "-classifier.rf.cat 10 ",  "-classifier.rf.var 0 ", "-classifier.rf.nbtrees 100 ",
                "-classifier.rf.acc 0.01 ", "-rand 0 ",
                "-io.confmatout C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/confmat_", i,".txt ",
                "-io.out C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/model_", i,".txt "))
  
  #try with computeconfusionmatrix... working but error when running kappa function (no nxn matrix?)
  #system(paste0(path_trainImage, "otbcli_ComputeConfusionMatrix ",
  #"-in C:/Users/Laura/Documents/Uni/Fernerkundung/ergebnisse/2018/rgboutimg1.tif ",
  #"-ref vector ",
  #"-ref.vector.in C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/training_areas_", i,".shp ",
  #"-ref.vector.field LN_New ","-nodatalabel 0 ", 
  #"-ram 128 ",
  #"-out C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/confmat_test/confmat_ccm_", i,".txt "))

  ctable<-read.table(paste0("C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/confmat_", i,".txt"), sep = ",", header = F)

  #generate output file
  kappa<-compKappa(ctable=ctable)
  print(kappa)
  kappa_out[i,1]<-class
  kappa_out[i,2]<-kappa
}
colnames(kappa_out)<-c("leftout", "kappa")
print(kappa_out)

#save output file
write.table(kappa_out, "C:/Users/Laura/Documents/Uni/Fernerkundung/Daten/LN_train/train_kappa/kappa_out_ccm.txt")


#make sure projection is correct
#training_areas <- spTransform(training_areas, CRS("+init=epsg:25832"))
#test_areas <- spTransform(test_areas, CRS("+init=epsg:25832"))

#make sure extent is correct
#ex <- extent(475927,5630630,478886,5633083)
#training_areas@bbox<-as.matrix(ex)
#test_areas@bbox<-as.matrix(ex)
#plot(training_areas)

```
